%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Mohamed Youssef Chlendi}} & Email: \href{mailto:}{youssef.chlendi@gmail.com}\\
  &
   Mobile:~~~+216 22 079 448 \\
  \href{https://github.com/youssefchlendi}{Github: ~~github.com/youssefchlendi} \\
  
  \href{https://www.linkedin.com/in/mohamed-youssef-chlendi/}{LinkedIn: ~~Mohamed Youssef Chlendi}
\end{tabular*}


	    
\vspace{-5pt}
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{~~~~~~~~~~~~PHP, JavaScript, TypeScript, Java, Python, SQL, HTML, CSS, C, C\#, Dart, Kotlin}
\resumeSubItem{Frameworks}{~~~~~~~~~~Laravel, Symfony, Spring Boot, ExpressJs, Flutter, React Native, .NET MAUI, .NET 5, LAMP, VueJs, Angular 10, Ionic, Bootstrap}
\resumeSubItem{Tools}{~~~~~~~~~~~~~~~~~~~~GIT, MySQL, POSTMAN, GitHub, ZenHub, Azure DevOps, Firebase, Figma, Adobe Illustrator, GDPicture, WebSockets}
\resumeSubItem{Database}{~~~~~~~~~~~~~~MySQL, MongoDB, SQL Server}
\resumeSubItem{Operating system}{~~Linux(Debian), Windows, macOS}
\resumeSubItem{Soft Skills}{~~~~~~~~~~~~~Leadership, Event Management, Time Management}
\resumeSubItem{Methodology}{~~~~~~~~Scrum}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
\resumeSubheading{NeoLedge, Zarzis, Tunisia}{Remote}
    {Software Developer}{May 2023 - Present}
    \resumeItemListStart
        \resumeItem{Enterprise Mobile Applications}
          {Developed and maintained enterprise mobile applications, integrating SOAP web services for seamless backend communication.}
        \resumeItem{PDF Signature System}
          {Designed and implemented a CLI for signing PDF files following the PADES-B standard using GDPicture.}
        \resumeItem{Cross-Platform Toolbox}
          {Created and published a toolbox wrapping the CLI for Windows and macOS, ensuring compatibility with ARM and Intel architectures.}
        \resumeItem{Installer Development}
          {Developed installers for the toolbox and its dependencies, supporting seamless deployment on Windows and macOS.}
        \resumeItem{Web Extension Integration}
          {Developed a system to make the CLI accessible from web applications using native messaging hosts and browser extensions compatible with major browsers.}
        \resumeItem{CI/CD Pipeline}
          {Prepared and maintained Azure DevOps CI/CD pipelines for seamless integration and deployment of new features.}
        \resumeItem{Electronic Signature System}
          {Integrated the extension into a web application to enable an online document signature system.}
        \resumeItem{Certification and Compliance}
          {Facilitated homologation of applications by conducting thorough tests and adaptations to meet eIDAS guidelines, achieving certification from TunTrust and ANCE Tunisia.}
          \resumeItem{System Integration Research}
    {Conducted extensive research to identify the most effective solutions for linking web applications with desktop environments. Evaluated multiple approaches, including:
      \begin{itemize}
        \item URI-based communication for straightforward and flexible integration.
        \item HTTPS client-side communication for secure and robust data exchange.
        \item WebSocket-based communication for real-time, bidirectional interaction between systems.
      \end{itemize}
    Implemented the selected solution to enable seamless interaction between web and desktop platforms, improving system efficiency and user experience.}
    \resumeItem{Mobile App Modernization R&D}
    {Led research and development efforts to modernize a legacy mobile app by migrating it from Xamarin to a more advanced technology. Conducted a detailed evaluation of potential solutions, including:
      \begin{itemize}
        \item \textbf{Flutter:} Evaluated for its fast development cycle, hot reload feature, and support for cross-platform UIs.
        \item \textbf{React Native:} Assessed for its extensive ecosystem, strong community support, and performance benefits through native modules.
        \item \textbf{.NET MAUI:} Analyzed for its integration with the .NET ecosystem, backward compatibility, and suitability for enterprise solutions.
      \end{itemize}
    Delivered a comprehensive report to management, outlining the pros and cons of each technology and providing strategic recommendations aligned with the organization's future scalability and technical goals.}

                  \resumeItem{Legacy Application Maintenance}
          {Maintained and enhanced a legacy UWP application to ensure continuous client support and stability.}

    \resumeItemListEnd
        {Technologies: C\#, .NET Core, CLI Development, Desktop Development, Extension Development, Electronic Signature, Web Development, Vue.js, Azure DevOps, Microsoft Azure}

\resumeSubheading{ NeoLedge, Zarzis, Tunisia  }{}
    {Mobile Developer (End of studies internship)}{Feb 2023 - May 2023}
    \resumeItemListStart
        \resumeItem{}
          {Contributed to the creation of a cross-platform mobile application for managing and signing electronic documents.}
          \resumeItem{}
          {Creation of NeoPDFViewer, an open-source file viewer, for seamless document visualization and interaction within the application.}
      \resumeItemListEnd
        {Technologies: Mobile development, Capacitor, Jest, Firebase, Framework Ionic, TypeScript, JavaScript, Scrum, Agile, Microsoft Azure}
        
\vspace{-5pt}
\resumeSubheading{ NeoLedge, Zarzis, Tunisia  }{Remote}
    {FrontEnd Developer (Internship)}{Jul 2022 - Nov 2022}
    \resumeItemListStart
        \resumeItem{}
          {Contributed to the existing NUI package by creating new components that will be used in future NeoLedge projects.}
          \resumeItem{}
          {Contribution to the development of a new Survey application for the company.}
      \resumeItemListEnd
        {Technologies: Vue 2.6, TypeScript, StoryBook, CSS, github, Scrum, Agile, Microsoft Azure, C#, .NET 5}
        
\vspace{-5pt}
    \resumeSubheading{ Scouts, Zarzis, Tunisia  }{Remote}
    {FullStack Developer/Product Owner }{Jul 2022 - Aug 2022}
    \resumeItemListStart
        \resumeItem{Needs analysis}
          {Reviewed the current system and uncovered its flaws.}
          \resumeItem{Managment}
          {Created user stories, managed and prioritized the product backlog.}
          \resumeItem{Development}
          {Developed and created parts of the system while maintaining high standards of code quality .}
          
      \resumeItemListEnd
        {Technologies: NuxtJs, Scrum, Agile, Vuetify, TypeScript, Laravel9, github, ZenHub, GitHub Ci/Cd Actions}
        
\vspace{-5pt}
 \resumeSubheading{ TunVita  }{Remote}
    {FullStack Developer (Internship)}{Jan 2022 - Feb 2022}
    \resumeItemListStart
        \resumeItem{Planning and needs analysis}
          {Reviewed the current employee management system and find the flaws.}
          \resumeItem{Desing of the system}
          {Designed the use case, the class and all necessary diagrams.}
          \resumeItem{Developmenent}{Developed the application using the Laravel/Vue stack while maintaining high standards of code quality and thoughtful application design.}
      \resumeItemListEnd
        {Technologies: Laravel 8, Vue 2.6, JavaScript, Bootstrap-vue, github}
        
\vspace{-5pt}

    \resumeSubheading{ TunVita  }{Remote}
    {FullStack Developer (Internship)}{Jul 2021 - Aug 2021}
    \resumeItemListStart
          \resumeItem{Front-end Development}{Developed a static website without and with template.}
          \resumeItem{Back-end Development}{Developed an adminPanel that manages (read, reply,
delete) the messages received from the contact form using PHP
and SQL.}
      \resumeItemListEnd
        {Technologies: HTML, CSS, Js, PHP, MySql, SQL}
        \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Higher Institue Of Informatics}{Ariana, Tunisia}
      {Master in Open Source Software Engineering}{Sep 2023 - June 2025}
      
    \resumeSubheading
      {Higher Institue Of Technlogical Studies}{Bizerte, Tunisia}
      {Bachelor in information system technology, excellent honors}{Sep 2020 - June 2023}
      
    \resumeSubHeadingListEnd
    
%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Bike tracking and after sales service}{(Oct 2022 -Jan 2023)
 Contributed to the development of the pixiimotors web/mobile application, which enables scooter owners to track and manage their motorcycles remotely, and set up an after-sales system enabling customers to communicate with the company using a ticketing system.
\\ Tech: SpringBoot, Nodejs, ExpressJs, MongoDB, Microservice, Angular, Flutter, GitHub}
\vspace{2pt}
\resumeSubItem{Scouts system}{(Jun 2022 - now)
 Contributed to the development of the Scout Volunteer Project, which is an application to manage registration and enrollment in the organization, manage monetary/material resources, and to allow users to create formal applications, schedule events and manage their groups.
\\ Tech: Nuxt, TypeScript, Vuetify, Laravel Zenhub, GitHub }
\vspace{2pt}
\resumeSubItem{ISETB - School management system
 }{(Mar 2022 - Jun 2021) 
 Contributed to the development of the ISETB application, which allows to manage all the actions that take place within the institute, as a member of the development team.
 \\\small{This project was developed in two different technology stacks, Laravel/vue and SpringBoot/Thymleaf.}
\\ Tech: VueJs2, JavaScript, Laravel, SpringBoot, Java, Thymleaf, Scrum, Agile, Zenhub, GitHub }

\resumeSubHeadingListEnd

%-----------LICENSES AND CERTIFICATIONS-----------------
\section{Licenses and Certifications}
\resumeSubHeadingListStart
    \resumeSubItem{Google Cloud Essentials Badge}
        {Google Cloud Education; Issued: Feb 2022; Certification ID: 1740267}
        {\href{https://www.cloudskillsboost.google/public_profiles/b6cf5253-6dac-4b50-8a0d-7129daad930b/badges/1740267}{View Credential}}
    \resumeSubItem{SQL Course Certificate}
        {Sololearn; Issued: Feb 2022; Certification ID: 20332926-1060}
        {\href{https://www.sololearn.com/certificates/course/en/20332926/1060/landscape/png}{View Credential}}
    \resumeSubItem{Scrum Fundamentals Certified}
        {SCRUMstudy - Accreditation Body for Scrum and Agile; Issued: Feb 2022; Certification ID: 900581}
        {\href{https://c46e136a583f7e334124-ac22991740ab4ff17e21daf2ed577041.ssl.cf1.rackcdn.com/Certificate/ScrumFundamentalsCertified-MohamedYoussefChlendi-900581.pdf}{View Credential}}
    \resumeSubItem{Java Course Certificate}
        {Sololearn; Issued: Jan 2022; Certification ID: 20332926-1068}
        {\href{https://www.sololearn.com/certificates/course/en/20332926/1068/landscape/png}{View Credential}}
    \resumeSubItem{JavaScript Course Certificate}
        {Sololearn; Issued: Jan 2022; Certification ID: 20332926-1024}
        {\href{https://www.sololearn.com/certificates/course/en/20332926/1024/landscape/png}{View Credential}}
    \resumeSubItem{PHP Course Certificate}
        {Sololearn; Certification ID: 1059-20332926}
        {\href{https://www.sololearn.com/Certificate/1059-20332926/pdf/}{View Credential}}
    \resumeSubItem{Financial Management Training}
        {ADDCI-UN; Issued: Aug 2018}
\resumeSubHeadingListEnd


%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Certificate of encouragement - Issued by head of IT department iset bizerte - Jan 2021}
\end{description}

\vspace{-2pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeItem
    {Vice-Chair}
    {RAS IEEE ISET Bizerte SB}
    \resumeItem
    {Media and Communication manager}
    {Tunisian SolidWorks
Users Group ISET Bizerte}
   
\vspace{5pt}
\resumeSubHeadingListEnd

\end{document}